Systematic Design of Optimal Low-Thrust Transfers for the Three-Body Problem \thanks{This research has been supported in part by NSF under the grants CMMI-1243000 (transferred from 1029551), CMMI-1335008, and CNS-1337722.}

### 2017-06-27 Response.tex

First, in terms of composition, large portions of the paper are spent on lengthy development of foundational work that is well-known within the astrodynamics community and available in textbooks. Secondly, the contributions and findings of the authors feel highly preliminary and do not seem to evaluate their method at significant depth.

While there are the beginnings of a good article within this manuscript, it is not sufficiently close to publishable form to be accepted.  I recommend that the paper be rejected and that the authors push their investigation a bit further.  The eventual publication should focus less on background and should provide more insight into the fundamental properties of their method, using more rigorously constructed and analyzed examples.

I can sympathize that there was quite a long road to get to the point of understanding this topic and generating results in it. I hope that the authors will not find this verdict too discouraging, as I believe that stronger results are well within their reach.

SPECIFIC FEEDBACK:
\begin{itemize}
    \begin{itshape}
*** Bloat
In the introduction, the exposition of the problem could be considerably condensed, given the venue of publication. Additionally, the somewhat sprawling discussion jumps back and forth, and many key points seem to be repeated more than necessary.  It needs to be organized into titled subsections with specific scope.
\end{itshape}

The introduction is reduced and many of the paragraphs have been reworded and combined. 
In addition, the extended discussion of the benefits of variational integrators is removeda.
In the interest of space/clarity the modified introduction is not copied here.

### 2017-06-27 manuscript.tex
Introduction simplified and reduced
Reviewer 2 Comment 1

>>>>

In short, the authors present a systematic method of generating optimal transfer orbits in the three-body problem.
Previous results in the design of optimal transfers have relied on suboptimal direct optimization methods and conventional integration techniques.
This paper provides a discrete optimal control formulation to generate the reachability set on a \Poincare section.
We derive and solve the Euler-Lagrange equations to generate the necessary conditions for an optimal solution.
This results in an optimal solution rather than the suboptimal solution typical of direct optimal control methods.
In addition, the use of a geometric integrators ensures numerical stability for long-duration orbit transfers and maintains this behavior with the addition of small magnitude control inputs.
Our computation of the reachable set allows for a simple metric of defining optimal trajectories.
We avoid the issues inherent in selecting a valid initial condition for optimization.
Rather, we choose a state on the reachability set which minimizes the distance toward the desired target.
We demonstrate these capabilities via two numerical examples simulating transfer trajectories in the Earth-Moon system.
